title: "Estimating proportions of unsolved homicides in selected American cities"
author: "Jessy Jiao"
date: "11/12/2018"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages, echo = FALSE, message=FALSE, warning=FALSE}
library(DT)
library(dplyr)
library(assertive)
library(tidyverse)
library(readr)
library(tidyr)
library(dplyr)
library(broom)
library(purrr)
library(ggplot2)
library(forcats)
library(ggthemes)
library(broom)
```

1. import the homecides data

```{r import}
url <- paste0("https://raw.githubusercontent.com/washingtonpost/", "data-homicides/master/homicide-data.csv")
homicides <- read.csv(url, header = T)
```

2. Create new columns (`city_name` and `unsolved`)

```{r city_name column}
homicides <- homicides %>% 
  mutate(city_name = paste(city, state, sep = ", ")) %>% 
  filter(city_name != "Tulsa, AL")
```


3. Create new data frame `unsolved`

```{r create unsolved table}
total_homicides <- homicides %>% 
  group_by(city_name) %>% 
  summarize(n()) %>% 
  rename(cases_total = `n()`)
unsolved_homicides <- homicides %>% 
  group_by(city_name) %>% 
  select(city_name, disposition) %>% 
  filter(str_detect(disposition, 
                    "Closed without arrest|Open/No arrest")) %>% 
  summarize(n()) %>% 
  rename(unsolved_cases = `n()`)
unsolved <- full_join(total_homicides, unsolved_homicides, by = "city_name")
kable(unsolved_by_city, n = 6)
```



4. Estimating proportion of unsolved homicides in Baltimore, MD 

```{r prop.test, message=FALSE, warning=FALSE, include= TRUE}
baltimore <- unsolved[unsolved$city_name == "Baltimore, MD",]
baltimore_prop <- prop.test(x = baltimore$unsolved_cases, 
          n = baltimore$cases_total,
          conf.level = 0.95)
kable(tidy(baltimore_prop) %>% 
  select(estimate,
         conf.low,
         conf.high))
```


```{r proportion of all cities}
all_unsolved <- unsolved %>% 
  mutate(prop_test = map2(unsolved_cases, cases_total, prop.test), 
         tidy_prop_test = map(prop_test, tidy)) %>% 
  unnest(tidy_prop_test, .drop = TRUE)
```

5. Estimate proportion of unsolved homicides in all listed cities


```{r proportion of all cities}
all_unsolved %>% 
  select(city_name, estimate, conf.low, conf.high) %>% 
  mutate(city_name = reorder(city_name, estimate)) %>% 
  ggplot(aes(x = estimate, y = city_name)) +
  geom_point(color = "white") +
  geom_errorbarh(xmin = all_unsolved$conf.low,
                 xmax = all_unsolved$conf.high,
                 height = 0,
                 color = "white") +
  scale_x_continuous(breaks = c(0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8),
                     label = c("20.0%", "30.0%", "40.0%", 
                               "50.0%", "60.0%", "70.0%", "80.0%")) +
  labs(x = "Percent of homicides that are unsolved",
       y = "") +
  ggtitle("Unsolved homicides by city",
          subtitle = "Bars show 95% confidence interval") +
  theme_dark()
```




